Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-24 proposal/prop.tex
prop.aux

\noindent A quantum probability measure can be easily constructed if
one knows the current state of the quantum system by using the Born
rule~\cite{Born1983,Mermin2007,Jaeger2007}.  Specifically, for each
pure normalized quantum state $\ket{\phi}$, the Born rule induces a
probability measure $\mu_{\phi}^{B}$ defined as
$\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}$. Conversely every probability
measure must be of this shape (accounting for the generalization to
mixed states).

>>>>

\noindent A quantum probability measure can be easily constructed if
one knows the current state of the quantum system by using the Born
rule~\cite{Born1983,Mermin2007,Jaeger2007}.  Specifically, for each
pure normalized quantum state $\ket{\phi}$, the Born rule induces a
probability measure $\mu_{\phi}^{B}$ defined as
$\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}$. The situation generalizes to
mixed states $\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
$\sum_{j=1}^{N}q_{j}=1$ in which case the generalized Born rule
induces a probability measure $\mu_{\rho}^{B}$ defined
as follows~\cite{peres1995quantum,544199,Jaeger2007}:
\[
\mu_{\rho}^{B}\left(P\right) = 
\Tr\left(\rho P\right) = 
\sideset{}{_{j=1}^{N}}\sum q_{j}\mu_{\phi_{j}}^{B}\left(P\right)
\]
Conversely every probability measure must be of this form.
